timesliced_random_cell_selection

### 2018-11-15 src/timesliced_random_cell_selection.Rmd
moving on to NAO and AMO

>>>>

basically what I did was use the selection -> select by attributes tool to find the points where NAFO_region = NA and then manually recode them (using the field calculator), and exported as a .csv.

```{r}
background_all <- read.csv("../output/bio/background_all_lonlat_nafo2.csv", header = TRUE)
head(background_all)
```

#original scientific name

create a column called "originalscientificname" and fill it with "Mallotus villosus ab"

```{r}
background_all$originalscientificname <- "Mallotus villosus ab"
head(background_all)
```

#NAO and AMO values
